# Intro to the Tidyverse

<https://learn.datacamp.com/courses/introduction-to-the-tidyverse>

## Data wrangling
The following info goes into how to select (filter), arrange, add, change (mutate) specific variables and observations. Install these two packages so codes below work properly:

    install.packages("gapminder")
    install.packages("dplyr")

**Loading the gapminder and dplyr packages**

```{r}
# Load the gapminder package
library(gapminder)
# Load the dplyr package
library(dplyr)

# Look at the gapminder dataset
gapminder
```

**Filter, Arrange, And Mutate Verbs**

<center>**Filter Verb**</center>

The `filter` verb extracts particular observations based on a condition. The `==`is to compare two values.

```{r}
# Filter for China in 2002
gapminder %>%
    filter(country == "China",year == 2002)
```

<center>**Arrange Verb**</center>

use arrange() to sort observations in ascending or descending order of a particular variable:

```{r}
# Sort in ascending order of lifeExp
gapminder %>%
    arrange(lifeExp)

# Sort in descending order of lifeExp
gapminder %>%
    arrange(desc(lifeExp))
```

<center>**Mutate Verb**</center>

`mutate()` changes or adds variables:

```{r}
# Use mutate to change lifeExp to be in months
gapminder %>%
    mutate(lifeExp = 12 * lifeExp)

# Use mutate to create a new column called lifeExpMonths
gapminder %>%
    mutate(lifeExpMonths = 12 * lifeExp) 
```

<center>**Combining Filter, Mutate, And Arrange**</center>

```{r}
# Filter, mutate, and arrange the gapminder dataset
gapminder %>%
    filter(year == 2007) %>%
        mutate(lifeExpMonths = 12 * lifeExp) %>%
    arrange(desc(lifeExpMonths))
```

## Data visualization

Make sure to load the `ggplot2` package. `ggplot2` will allow the visualization of data into graphs.

```{r}
library(ggplot2)

gapminder_1952 <- gapminder %>%
  filter(year == 1952)

#Create a plot to compare population and life expectancy
ggplot(gapminder_1952, aes(x = pop, y = lifeExp)) + geom_point()
```

`geom_point()` stands for "geometric", and the "point" tells R that it's a scatter plot. `aes()` stands for aesthetic.
The data is too cramped up to the left of the plot so use "log scales" to distribute the data better.

***Log Scale**

```{r}
# Scatter plot comparing pop and gdpPercap, with both axes on a log scale
ggplot(gapminder_1952, aes(x = pop, y = gdpPercap)) + geom_point() +scale_x_log10() + scale_y_log10()
```

the newly added "log_scales" has created a better looking graph by adjusting the scale of the x-axis.

**Additional Aesthetic Functions**

<center>**Color And Size**</center>

Adding color to a scatter plot can be used to show which continent each point in a scatter plot represents. Then, adding size can be used to show the magnitude of each observations:

```{r}
# Add the color, and size aesthetics to represent the continents and the country's gdpPercap
ggplot(gapminder_1952, aes(x = pop, y = lifeExp, color = continent, size = gdpPercap)) +
  geom_point() +
  scale_x_log10()
```

<center>**Faceting/Subgraphs**</center>

Use `facet_wrap(~ )` function to divide a graph into subplots based on one of its variables:

```{r}
# Scatter plot comparing pop and lifeExp, faceted by continent
ggplot(gapminder_1952, aes(x = pop, y = lifeExp)) + geom_point() + scale_x_log10() + facet_wrap(~ continent)
```

## Grouping and summarizing

**Summarize Verb**

The function `summarize()` combines many observations from the same variable into one:

```{r}
# Filter for 1957 then summarize the median life expectancy and the maximum GDP per capita
gapminder %>%
    filter(year == 1957) %>%
        summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
```

In this case, the code summarized the median life expectancy and maximum GDP/capita of all the countries and conitents from 1957. 

**Group_by Verb**

This function `group_by()` is basically an advanced version of the `filter()` function. If the `filter()` along with the `summarize()` functions can summarize observations of variable(s) one of each filtered type at a time, then `group_by()` function can run the same calculations for all the observation units:

```{r}
# Find median life expectancy and maximum GDP per capita in each year
gapminder %>%
    group_by(year) %>%
        summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
```

**Visualizing the dataset**

Assigning the dataset to a variable then plug it in to the `ggplot2` to make a graph:
```{r}
# Summarize medianGdpPercap within each continent within each year: by_year_continent
by_year_continent <- gapminder %>%
        group_by(continent, year) %>%
            summarize(medianGdpPercap = median(gdpPercap))

# Plot the change in medianGdpPercap in each continent over time
ggplot(by_year_continent, aes(x = year, y = medianGdpPercap, color = continent)) + geom_point() + expand_limits(y = 0)
```

## Types of visualizations

**Line Plot**

A line plot is useful for visualizing trends over time. Use `geom_line()` to create a line plot instead of `geom_point()` to create a scatter plot. The function `expand_limits(y = 0)` tells the y-axis to start from `0`:

```{r}
# Create a line plot showing the change in medianGdpPercap by continent over time
ggplot(by_year_continent, aes(x = year, y = medianGdpPercap, color = continent)) + geom_line() + expand_limits(y = 0)
```

**Bar Plot**

A bar plot is useful for visualizing summary statistics. use `geom_col()` to create a bar plot:

```{r}
# Filter for observations in the Oceania continent in 1952
oceania_1952 <- gapminder %>%
    filter(continent == "Oceania", year == 1952)

# Create a bar plot of gdpPercap by country
ggplot(oceania_1952, aes(x = country, y = gdpPercap)) + geom_col()
```

**Histogram**

A histogram is useful for examining the distribution of a numeric variable. Every bar represents a `bin` of a variable, and the height of the bar represents how many observations fall into that `bin`. Use `geom_histogram()` to create a histogram:

```{r}
gapminder_1952 <- gapminder %>%
  filter(year == 1952) %>%
  mutate(pop_by_mil = pop / 1000000)

# Create a histogram of population (pop_by_mil)
ggplot(gapminder_1952, aes(x = pop_by_mil)) + geom_histogram(bins = 50)
```

**Boxplot**

A boxplot is useful for comparing a distribution of values across several groups.

```{r}
# Create a boxplot comparing gdpPercap among continents
ggplot(gapminder_1952, aes(x = continent, y = gdpPercap)) + geom_boxplot() + scale_y_log10()

```

**How To Add A Title To A Graph**

Use `ggtitle()` function to add a title to a graph:

```{r}
# Add a title to this graph: "Comparing GDP per capita across continents"
ggplot(gapminder_1952, aes(x = continent, y = gdpPercap)) +
  geom_boxplot() +
  scale_y_log10() +
  ggtitle("Comparing GDP per capita across continents")
```

