# Working with Data in the Tidyverse

<https://learn.datacamp.com/courses/working-with-data-in-the-tidyverse>

## Explore your data

Load the `readr` package for every session so things work properly:

```{r}
library(dplyr)
library(readr)
election <- read_csv("http://faculty.baruch.cuny.edu/geoportal/data/county_election/elpo12p010g.csv")
election

#To skip lines from the top, start from the 2nd line for example, use "skip = 1" after comma in read_csv(...,)
```

`readr` is for rectangular data with extensions like: `.csv`, .tsv, `.fwf`, and `.log`

`read_csv()` function to read a csv file.

`readxl()` to read Microsoft Excel files.

**Assign Missing Values**

The `read_csv()` function also has an `na` argument, which allows you to specify value(s) that represent missing values in your data. 
The default values for the na argument are `c("", "NA")`, so both are recorded as missing (`NA`) in R. When you read in data, you can add additional values like the string `"UNKNOWN"` to a vector of missing values using the `c()` function to combine multiple values into a single vector.

The `is.na()` function is also helpful for identifying rows with missing values for a variable.

    read_csv("electiomn.csv", skip = 1, na = c("", "NA", "A new unspecified variable"))

    election %>% filter(is.na(variable you want to filter to find na))

The election data didn't have any observations classified as a `na` so the example above is for when assuming there's a missing value you want to filter/find. 

**How to list out all the variables of a dataset**

Use `glimpse()` to list out the hidden variables in the dataset:

```{r}
glimpse(election)
```

Combine `glimpse()` with other functions in a sequence using the pipe (`%>%`) operator. For example, function like `arrange`:

```{r}
election %>% 
  arrange(OBAMA) %>% 
  glimpse() # no argument needed here
```
Compare to the two code chunks, this arraged data shows the ascending order of `OBAMA`.

**How to get a list of summarized statistics of all the variables of a dataset**

Use `skim()` to list the standard statistics of the variables:

```{r}
library(skimr)
        
skim(election)
```

You can combine `skim()` with other functions in a sequence using the pipe (%>%) operator. For example, use function `summary()` to find how many variables of each type are in the dataset:

```{r}
election %>% 
  skim() %>%  # no argument needed here
  summary() # no argument needed here
```

**Count the data**

<center>Distinct()</center>

Use `distinct()` to find out how many different type of observations are there in one variable. To find out how many distinct states are there in the `STATE` variable:


```{r}
election %>%
  distinct(STATE)
``` 

<center>Count()</center>

`count()` adds a new column named `n` to store the counts. this `count` function basically does the `group_by` and `summarize` for you. count the number of `counties` in each `state`:

```{r}
election %>%
  count(STATE)
```

Adapt the code to count by a logical condition instead:

```{r}
election %>%
  count(WINNER == "Obama")
```

## Tame your data

**Cast Column Types**
To assign or change the type of the columns in the dataset.

<center>**Cast A Column To a Date**</center>

Use `parse_date("2012-14-08", format = "%Y-%d-%m")` then use `col_date(format = "%Y-%d-%m")` within cols() as the col_types argument of read_csv().

    parse_date("2012-14-08", format = "%Y-%d-%m")
    
    read_csv(...., col_types = cols( variale_name = col_date(format = "%Y-%d-%m")))

<center>**Cast A Column To a Number**</center>

    read_csv(...., variable_name = col_number())

Sometimes, there are `na` contained in the observations which would create errors while trying to cast. 

Diagnose parsing problems using a new `readr` function called `problems()`. Using `problems()` on a result of `read_csv()` will show you the rows and columns where parsing error occurred, what the parser expected to find (for example, a number), and the actual value that caused the parsing error.

<center>**Cast A Column As A Factor**</center>

Factors are categorical variables, where the possible values are a fixed and known set.

Use `parse_factor()` to parse variables and `col_factor()` to cast columns as categorical. Both functions have a `levels` argument that is used to specify the possible values for the factors. When `levels` is set to `NULL`, the possible values will be inferred from the unique values in the dataset. Alternatively, you can pass a list of possible values.

    read_csv(...., variable_name = col_factor(levels = NULL))
    
For more details, go to the [Cast A Factor And Examine Levels](https://econ380w21.github.io/bpAlNw1Ae7YwY9H3f/working-with-data-in-the-tidyverse.html#transform-your-data) section of this chapter.

**Recode Values**

Use `recode()` function in the `dplyr` package. The `recode` function is to re-name the observations into something easier to understand.

<center>**Recode A Character Variable**</center>

```{r}
election_CA <- election %>% filter(STATE == "CA")

election_CA %>% 
  mutate(STATE = recode(STATE, "CA" = "California"))
```

<center>**Recode A Numeric Variable Into Factor **</center>

Dummy variables are often used in data analysis to bin a variable into one of two categories to indicate the absence or presence of something. Dummy variables take the value `0` or `1` to stand for, for example, `V_engine` or `S_engine`. 


```{r}
Car_engine <- mtcars[1:10,] %>%
  mutate(Engine_Type = recode(vs, "0" = "V_engine", .default =  "S_engine")) %>%
    select(vs, Engine_Type, everything(), -"carb") 

Car_engine

#Since there're only 2 distinct levels, the "1" = "S_engine" can be coded as ".default".
```

**Select And Reorder Variables**

Selecting a subset of columns to print can help check that a `mutate()` worked as expected, and rearranging columns next to each other can help spot obvious errors in data entry.

The `select()` **helpers** are functions that allow selection of variables based on their names:

```{r echo=FALSE}
Function <- c("starts_with()", "ends_with()", "contains()", "matches()", "num_range()", "one_of()", "everything()", "last_col()")
Usage <- c("starts with a prefix", "ends with a prefix", "contains a literal string", "matches a regular expression", "a numerical range like x01, x02, x03.", "variables in character vector.", "all variables.", "last variable, possibly with an offset.")
data.frame(Function, Usage)
```

```{r}
# Move vs, and Engine_type to front and show only from mpg to drat:
Car_engine[1:10,] %>% 
   select(vs, Engine_Type, mpg:drat) 
```

**Reformat Variable Names**

To change names **WITHOUT** changing the order of the variables, write `everything()` first in the `select()` function.
The function `clean_names()` takes an argument case that can be used to convert variable names to other cases, like `"upper_camel"` or `"all_caps"`.

use `clean_names()` from the `janitor` package to convert all variable names to snake_case.

    install.packages("janitor")

```{r}
library(janitor)

election[1:10,] %>% clean_names("snake")

#Notice how all the variables are lower_case now.
```

**How To Rename, Subset, And Reorder Variables At Once**

To rename, then subset (choose to show only selected) , and finally reorder variables in one code line, use `select()`.

    dataset_name %>% select( new_variable_name_ = starts_with("old_name") ) 

This code will find all variables in `dataset_name` whose names start with `old_name`, then rename each variable as `new_name_<N>`, where `N` is a number. If `dataset_name` has variables `oldname`, `oldname_v1`, `oldname3`, then the code will replace these names with `new_name_1`, `new_name_2`, `new_name_3`.


The arguments inputted into `select()` determines what R will show. And, the order of the arguments inputted will determine how the resulting order of the variables will be.

```{r}
election[1:10,] %>% 
  select(Precint_ = contains("PCT"), everything(), -"group")
```
This example, the `PCT_name` has been replaced into `Precint_<N>`. The `Precint_` is first in the `select()` function so it will be shown first, then next is `everything()` so everything else will be shown the way it is, then exclude the `group` variable.

## Tidy your data

**gather()**

    ?gather

The `gather()` function collapses multiple columns into two columns. It reshapes the dataset from wide to long, it reduces the number of columns and increases the number of rows.

```{r}
library(tidyr)

Car_engine[1:2,] %>%
  gather(key = "measurements", value = "specs", mpg:hp) %>%
    select(measurements, specs)

```

**seperate()**

Within a tidy dataset, a column should only represent only one variable, but if observations from that variable contains two distinct type of info, we can seperate it with `seperate()`.

This is an example for the code before/after using the `seperate` funtion:

    week_ratings
    
       series episode viewers_7day
       <fct>  <chr>          <dbl>
     1 1      e1_7day         2.24
     2 2      e1_7day         3.1 
     3 3      e1_7day         3.85
     4 4      e1_7day         6.6 
     5 5      e1_7day         8.51
     6 6      e1_7day        11.6 
     7 7      e1_7day        13.6 
     8 8      e1_7day         9.46
     9 1      e2_7day         3   
    10 2      e2_7day         3.53
    
    week_ratings <- ratings2 %>% 
        select(series, ends_with("7day")) %>% 
        gather(episode, viewers_7day, ends_with("7day"), 
               na.rm = TRUE) %>%
    	# Edit to separate key column and drop extra
        separate(episode, into = c("episode","day")) 
        
    week_ratings
    
       series episode   day viewers_7day
       <fct>  <chr>   <chr>         <dbl>
     1 1      e1      7day           2.24
     2 2      e1      7day           3.1 
     3 3      e1      7day           3.85
     4 4      e1      7day           6.6 
     5 5      e1      7day           8.51
     6 6      e1      7day          11.6 
     7 7      e1      7day          13.6 
     8 8      e1      7day           9.46
     9 1      e2      7day           3   
    10 2      e2      7day           3.53


**Unite Columns**

In the `tidyr` package, the opposite of `separate()` is` unite()`. Sometimes you need to paste values from two or more columns together to tidy. Here is an example usage for `unite()`:

    data %>%
        unite(new_var, old_var1, old_var2)
To apply the function into the `election` data, merge the `COUNTY` into the `STATE`: 

```{r}
election_CA[1:5,] %>%
  unite(LOCATION, STATE, COUNTY, sep = ", ")
```

**spread()**

Spreading reshapes the data from long to wide, adds columns and shrinks the rows.

```{r tidy_ratings_all, include=FALSE}
tidy_ratings_all <- data.frame(structure(list(series = c(1, 2, 3, 4, 5, 6, 7, 8, 6, 7, 8, 1, 
2, 3, 4, 5, 6, 7, 8, 6, 7, 8, 1, 2, 3, 4, 5, 6, 7, 8, 7, 8, 1, 
2, 3, 4, 5, 6, 7, 8, 6, 7, 8, 1, 2, 3, 4, 5, 6, 7, 8, 6, 7, 8, 
1, 2, 3, 4, 5, 6, 7, 8, 6, 7, 8, 2, 3, 4, 5, 6, 7, 8, 6, 7, 8, 
2, 3, 4, 5, 6, 7, 8, 6, 7, 8, 3, 4, 5, 6, 7, 8, 6, 7, 8, 3, 4, 
5, 6, 7, 8, 6, 7, 8), episode = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 
1, 1, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, 3, 
3, 3, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 5, 5, 5, 5, 5, 5, 5, 5, 
5, 5, 5, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 7, 7, 7, 7, 7, 7, 7, 
7, 7, 7, 8, 8, 8, 8, 8, 8, 8, 8, 8, 8, 9, 9, 9, 9, 9, 9, 9, 9, 
9, 10, 10, 10, 10, 10, 10, 10, 10, 10), days = c(7, 7, 7, 7, 
7, 7, 7, 7, 28, 28, 28, 7, 7, 7, 7, 7, 7, 7, 7, 28, 28, 28, 7, 
7, 7, 7, 7, 7, 7, 7, 28, 28, 7, 7, 7, 7, 7, 7, 7, 7, 28, 28, 
28, 7, 7, 7, 7, 7, 7, 7, 7, 28, 28, 28, 7, 7, 7, 7, 7, 7, 7, 
7, 28, 28, 28, 7, 7, 7, 7, 7, 7, 7, 28, 28, 28, 7, 7, 7, 7, 7, 
7, 7, 28, 28, 28, 7, 7, 7, 7, 7, 7, 28, 28, 28, 7, 7, 7, 7, 7, 
7, 28, 28, 28), viewers = c(2.24, 3.1, 3.85, 6.6, 8.51, 11.62, 
13.58, 9.46, 11.73, 13.86, 9.72, 3, 3.53, 4.6, 6.65, 8.79, 11.59, 
13.45, 9.23, 11.84, 13.74, 9.53, 3, 3.82, 4.53, 7.17, 9.28, 12.01, 
13.01, 8.68, 13.38, 9.06, 2.6, 3.6, 4.71, 6.82, 10.25, 12.36, 
13.29, 8.55, 12.67, 13.88, 8.87, 3.03, 3.83, 4.61, 6.95, 9.95, 
12.39, 13.12, 8.61, 12.63, 13.33, 8.98, 2.75, 4.25, 4.82, 7.32, 
10.13, 12, 13.13, 8.61, 12.26, 13.41, 8.91, 4.42, 5.1, 7.76, 
10.28, 12.35, 13.45, 9.01, 12.58, 13.72, 9.32, 5.06, 5.35, 7.41, 
9.023, 11.09, 13.26, 8.95, 11.35, 13.45, 9.19, 5.7, 7.41, 10.67, 
12.65, 13.44, 9.03, 12.78, 13.65, 9.16, 6.74, 9.45, 13.51, 15.05, 
15.9, 10.04, 15.16, 16.03, 10.13)), .Names = c("series", "episode", 
"days", "viewers"), row.names = c(NA, -103L), class = c("tbl_df", 
"tbl", "data.frame")))
```

```{r}
tidy_ratings_all[1:10,]
```

```{r}
tidy_ratings_all %>% 
	# Count viewers by series and days
    count(series, days, wt = viewers) %>%
	# Adapt to spread counted values
    spread(days, n, sep = "_")
```

## Transform your data

**How To Create A Range-filtered Column**

Use case_when() to create a new column that represents a given range:

```{r include=FALSE}
bakers <- data.frame(structure(list(series = structure(c(1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 3L, 
3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 4L, 4L, 4L, 4L, 4L, 
4L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 
5L, 5L, 5L, 5L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 
7L, 7L, 7L, 7L, 7L, 7L, 7L, 7L, 7L, 7L, 7L, 7L, 8L, 8L, 8L, 8L, 
8L, 8L, 8L, 8L, 8L, 8L, 8L, 8L), class = "factor", .Label = c("1", 
"2", "3", "4", "5", "6", "7", "8")), baker_full = c("Annetha Mills", 
"David Chambers", "Edward \"Edd\" Kimber", "Jasminder Randhawa", 
"Jonathan Shepherd", "Lea Harris", "Louise Brimelow", "Mark Whithers", 
"Miranda Gore Browne", "Ruth Clemens", "Ben Frazer", "Holly Bell", 
"Ian Vallance", "Janet Basu", "Jason White", "Joanne Wheatley", 
"Keith Batsford", "Mary-Anne Boermans", "Robert Billington", 
"Simon Blackwell", "Urvashi Roe", "Yasmin Limbert", "Brendan Lynch", 
"Cathryn Dresser", "Danny (Daniele) Bryden", "James Morton", 
"John Whaite", "Manisha Parmar", "Natasha Stringer", "Peter Maloney", 
"Ryan Chong", "Sarah-Jane Willis", "Victoria Chester", "Stuart Marston-Smith", 
"Ali Imdad", "Beca Lyne-Pirkis", "Christine Wallace", "Deborah Manger", 
"Frances Quinn", "Glenn Cosby", "Howard Middleton", "Kimberley Wilson", 
"Lucy Bellamy", "Mark Onley", "Robert Smart", "Ruby Tandoh", 
"Toby Waterworth", "Chetna Makan", "Claire Goodwin", "Diana Beard", 
"Enwezor Nzegwu", "Iain Watters", "Jordan Cox", "Kate Henry", 
"Luis Troyano", "Martha Collison", "Nancy Birtwhistle", "Norman Calder", 
"Richard Burr", "Alvin Magallanes", "Dorret Conway", "Flora Shedden", 
"Ian Cumming", "Marie Campbell", "Mat Riley", "Nadiya Hussain", 
"Paul Jagger", "Sandy Docherty", "Stu Henshall", "Tamal Ray", 
"Ugnė Bubnaityte", "Andrew Smyth", "Benjamina Ebuehi", 
"Candice Brown", "Jane Beedle", "Kate Barmby", "Lee Banfield", 
"Louise Williams", "Michael Georgiou", "Rav Bansal", "Selasi Gbormittah", 
"Tom Gilliford", "Valerie \"Val\" Stones", "Chris Geiger", "Flo Atkins", 
"James Hillery", "Julia Chernogorova", "Kate Lyon", "Liam Charles", 
"Peter Abatan", "Sophie Faldo", "Stacey Hart", "Steven Carter-Bailey", 
"Tom Hetherington", "Chuen-Yan \"Yan\" Tsou"), baker = c("Annetha", 
"David", "Edd", "Jasminder", "Jonathan", "Lea", "Louise", "Mark", 
"Miranda", "Ruth", "Ben", "Holly", "Ian", "Janet", "Jason", "Joanne", 
"Keith", "Mary-Anne", "Robert", "Simon", "Urvashi", "Yasmin", 
"Brendan", "Cathryn", "Danny", "James", "John", "Manisha", "Natasha", 
"Peter", "Ryan", "Sarah-Jane", "Victoria", "Stuart", "Ali", "Beca", 
"Christine", "Deborah", "Frances", "Glenn", "Howard", "Kimberley", 
"Lucy", "Mark", "Robert", "Ruby", "Toby", "Chetna", "Claire", 
"Diana", "Enwezor", "Iain", "Jordan", "Kate", "Luis", "Martha", 
"Nancy", "Norman", "Richard", "Alvin", "Dorret", "Flora", "Ian", 
"Marie", "Mat", "Nadiya", "Paul", "Sandy", "Stu", "Tamal", "Ugnė", 
"Andrew", "Benjamina", "Candice", "Jane", "Kate", "Lee", "Louise", 
"Michael", "Rav", "Selasi", "Tom", "Val", "Chris", "Flo", "James", 
"Julia", "Kate", "Liam", "Peter", "Sophie", "Stacey", "Steven", 
"Tom", "Yan"), age = c(30, 31, 24, 45, 25, 51, 44, 48, 37, 31, 
31, 31, 40, 63, 19, 41, 31, 45, 25, 31, 40, 43, 63, 27, 45, 21, 
23, 27, 36, 43, 38, 28, 50, 26, 25, 31, 66, 51, 31, 37, 51, 30, 
38, 37, 54, 20, 30, 35, 31, 69, 39, 31, 32, 41, 42, 17, 60, 66, 
38, 37, 53, 19, 41, 66, 37, 30, 49, 49, 35, 29, 32, 25, 23, 31, 
61, 37, 67, 46, 20, 28, 30, 26, 66, 50, 71, 46, 21, 29, 19, 52, 
33, 42, 34, 29, 46), occupation = c("Single mother", "Entrepreneur", 
"Debt collector for Yorkshire Bank", "Assistant Credit Control Manager", 
"Research Analyst", "Retired", "Police Officer", "Bus Driver", 
"Food buyer for Marks & Spencer", "Retail manager/Housewife", 
"Graphic Designer", "Advertising executive", "Fundraiser for English Heritage", 
"Teacher of Modern Languages", "Civil Engineering Student", "Housewife", 
"House husband", "Housewife", "Photographer", "Rugby Coach", 
"Head of Marketing", "Childminder", "Recruitment consultant", 
"Shop assistant", "Intensive care consultant", "Medical student", 
"Law student", "Nursery nurse", "Midwife", "Sales manager", "Photographer", 
"Vicar's wife", "CEO of the charity Plantlife", "PE teacher", 
"Charity worker", "Military Wives' Choir Singer", "Director of an engraving company", 
"Dentist", "Children's Clothes Designer", "English Teacher", 
"Council Worker", "Psychologist", "Horticulturist", "Carpenter & Kitchen Fitter", 
"Space Satellite Designer", "History of Art and Philosophy Student", 
"Web Programmer", "Fashion designer", "Speech therapist", "Women's Institute (WI) judge", 
"Business consultant", "Construction engineer", "IT manager", 
"Furniture restorer", "Graphic designer", "Student", "Retired practice manager", 
"Retired naval officer", "Builder", "Nurse", "Accountant", "Art gallery assistant", 
"Travel photographer", "Retired", "Fire fighter", "Full-time mother", 
"Prison governor", "Child welfare officer", "Professional musician", 
"Trainee anaesthetist", "PA and administrator", "Aerospace engineer", 
"Teaching assistant", "PE teacher", "Garden designer", "Nurse", 
"Pastor", "Hairdresser", "Student", "Student support", "Client service associate", 
"Project engagement manager", "Semi-retired, Substitute teacher", 
"Software developer", "Retired", "Banker", "Aviation Broker", 
"Health and safety inspector", "Student", "IT programme manager", 
"Former army officer and trainee stuntwoman", "Former school teacher", 
"Marketer", "Architect", "Laboratory research scientist"), hometown = c("Essex", 
"Milton Keynes", "Bradford", "Birmingham", "St Albans", "Midlothian, Scotland", 
"Manchester", "South Wales", "Midhurst, West Sussex", "Poynton, Cheshire", 
"Northampton", "Leicester", "Dunstable, Bedfordshire", "Formby, Liverpool", 
"Croydon", "Ongar, Essex", "Arlesey, Bedfordshire", "Kidderminster, Worcestershire", 
"London", "Norfolk", "Enfield, London", "West Kirby, The Wirral", 
"Sutton Coldfield", "Pease Pottage, West Sussex", "Sheffield", 
"Hillswick, Shetland Islands", "Wigan", "Leicester", "Tamworth, Staffordshire", 
"Windsor, Berkshire", "Bristol", "Bewbush, West Sussex", "Somerset", 
"Lichfield, Staffordshire", "Saltley, Birmingham", "Aldershot, Hampshire", 
"Didcot, Oxfordshire", "Peterborough", "Market Harborough, Leicestershire", 
"Teignmouth, Devon", "Sheffield", "London", "Grimsby, Lincolnshire", 
"Milton Keynes", "Melbourn, Cambridgeshire", "Southend, Essex", 
"Reading, Berkshire", "Broadstairs, Kent", "Ashton on Mersey, Trafford", 
"Alkington, Shropshire", "Portsmouth, Hampshire", "London / Belfast", 
"Sneinton, Nottingham", "Brighton, East Sussex", "Poynton, Cheshire", 
"Ascot, Berkshire", "Barton-Upon-Humber, Lincolnshire", "Portknockie, Moray", 
"Mill Hill, London", "Bracknell, Berkshire", "Penwortham, Lancashire", 
"Dunkeld, Perth and Kinross", "Great Wilbraham, Cambridgeshire", 
"Auchterarder, Perthshire", "London", "Leeds / Luton", "Swansea, Wales", 
"Yeadon, West Yorkshire", "Guildford, Surrey", "Manchester", 
"Woodford, London", "Derby / Holywood, County Down", "South London", 
"Barton-Le-Clay, Bedfordshire", "Beckenham", "Brooke, Norfolk", 
"Bolton", "Cardiff", "Durham", "Erith", "London", "Rochdale", 
"Yeovil", "Bristol", "Merseyside", "Brentwood, Essex", "Crawley, West Sussex", 
"Merseyside", "North London", "Southend, Essex", "West Molesey, Surrey", 
"Radlett, Hertfordshire", "Watford, Hertfordshire", "Edinburgh", 
"North London"), baker_last = c("Mills", "Chambers", "Kimber", 
"Randhawa", "Shepherd", "Harris", "Brimelow", "Whithers", "Browne", 
"Clemens", "Frazer", "Bell", "Vallance", "Basu", "White", "Wheatley", 
"Batsford", "Boermans", "Billington", "Blackwell", "Roe", "Limbert", 
"Lynch", "Dresser", "Bryden", "Morton", "Whaite", "Parmar", "Stringer", 
"Maloney", "Chong", "Willis", "Chester", "Marston-Smith", "Imdad", 
"Lyne-Pirkis", "Wallace", "Manger", "Quinn", "Cosby", "Middleton", 
"Wilson", "Bellamy", "Onley", "Smart", "Tandoh", "Waterworth", 
"Makan", "Goodwin", "Beard", "Nzegwu", "Watters", "Cox", "Henry", 
"Troyano", "Collison", "Birtwhistle", "Calder", "Burr", "Magallanes", 
"Conway", "Shedden", "Cumming", "Campbell", "Riley", "Hussain", 
"Jagger", "Docherty", "Henshall", "Ray", "Bubnaityte", "Smyth", 
"Ebuehi", "Brown", "Beedle", "Barmby", "Banfield", "Williams", 
"Georgiou", "Bansal", "Gbormittah", "Gilliford", "Stones", "Geiger", 
"Atkins", "Hillery", "Chernogorova", "Lyon", "Charles", "Abatan", 
"Faldo", "Hart", "Carter-Bailey", "Hetherington", "Tsou"), baker_first = c("Annetha", 
"David", "Edward", "Jasminder", "Jonathan", "Lea", "Louise", 
"Mark", "Miranda", "Ruth", "Ben", "Holly", "Ian", "Janet", "Jason", 
"Joanne", "Keith", "Mary-Anne", "Robert", "Simon", "Urvashi", 
"Yasmin", "Brendan", "Cathryn", "Danny", "James", "John", "Manisha", 
"Natasha", "Peter", "Ryan", "Sarah-Jane", "Victoria", "Stuart", 
"Ali", "Beca", "Christine", "Deborah", "Frances", "Glenn", "Howard", 
"Kimberley", "Lucy", "Mark", "Robert", "Ruby", "Toby", "Chetna", 
"Claire", "Diana", "Enwezor", "Iain", "Jordan", "Kate", "Luis", 
"Martha", "Nancy", "Norman", "Richard", "Alvin", "Dorret", "Flora", 
"Ian", "Marie", "Mat", "Nadiya", "Paul", "Sandy", "Stu", "Tamal", 
"Ugnė", "Andrew", "Benjamina", "Candice", "Jane", "Kate", 
"Lee", "Louise", "Michael", "Rav", "Selasi", "Tom", "Valerie", 
"Chris", "Flo", "James", "Julia", "Kate", "Liam", "Peter", "Sophie", 
"Stacey", "Steven", "Tom", "Chuen-Yan"), star_baker = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 1, 2, 1, 0, 0, 0, 0, 0, 1, 2, 
0, 1, 3, 1, 0, 0, 0, 1, 0, 1, 0, 0, 0, 2, 0, 1, 0, 0, 2, 0, 0, 
1, 3, 0, 1, 0, 0, 0, 0, 0, 1, 1, 0, 1, 0, 5, 0, 0, 0, 3, 1, 1, 
3, 0, 0, 0, 1, 0, 2, 1, 3, 1, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0, 0, 
1, 1, 1, 0, 2, 1, 3, 0, 0), technical_winner = c(0, 0, 2, 0, 
1, 0, 0, 0, 2, 0, 1, 2, 0, 1, 1, 3, 0, 0, 0, 0, 0, 0, 2, 1, 0, 
5, 1, 0, 0, 0, 0, 1, 0, 0, 0, 1, 1, 0, 1, 1, 0, 3, 0, 0, 1, 2, 
0, 1, 0, 0, 0, 0, 0, 1, 1, 2, 3, 0, 2, 0, 1, 1, 1, 0, 1, 4, 1, 
0, 0, 0, 1, 2, 1, 1, 2, 1, 0, 0, 0, 0, 1, 1, 1, 0, 0, 0, 0, 1, 
0, 0, 2, 2, 3, 0, 2), technical_top3 = c(1, 1, 4, 2, 1, 0, 0, 
0, 4, 2, 3, 5, 1, 1, 2, 4, 0, 4, 2, 0, 0, 2, 6, 4, 5, 7, 6, 0, 
0, 1, 0, 1, 0, 0, 0, 3, 2, 0, 7, 3, 0, 5, 1, 0, 3, 6, 0, 5, 0, 
0, 0, 0, 0, 2, 7, 5, 7, 0, 4, 1, 1, 7, 6, 1, 1, 4, 3, 0, 0, 4, 
2, 5, 4, 7, 5, 1, 0, 0, 1, 1, 3, 2, 1, 0, 0, 3, 3, 3, 3, 0, 6, 
4, 6, 0, 2), technical_bottom = c(1, 3, 1, 2, 2, 1, 1, 0, 1, 
2, 1, 3, 2, 6, 3, 4, 1, 4, 3, 2, 3, 4, 4, 4, 4, 3, 4, 5, 1, 1, 
7, 6, 3, 4, 4, 6, 6, 3, 3, 4, 6, 5, 1, 3, 2, 4, 1, 4, 1, 4, 2, 
4, 3, 5, 3, 3, 3, 5, 6, 5, 2, 2, 4, 1, 6, 6, 5, 4, 1, 6, 3, 5, 
4, 3, 5, 3, 1, 2, 2, 5, 6, 5, 4, 2, 3, 2, 3, 7, 5, 1, 4, 5, 4, 
4, 5), technical_highest = c(2, 3, 1, 2, 1, 10, 4, NA, 1, 2, 
1, 1, 2, 1, 1, 1, 12, 2, 3, 9, 7, 2, 1, 1, 2, 1, 1, 5, 12, 3, 
5, 1, 4, 7, 5, 1, 1, 8, 1, 1, 5, 1, 2, 5, 1, 1, 13, 1, 8, 5, 
9, 4, 6, 1, 1, 1, 1, 4, 1, 2, 1, 1, 1, 3, 1, 1, 1, 4, 11, 2, 
1, 1, 1, 1, 1, 1, 11, 9, 3, 3, 1, 1, 1, 11, 7, 2, 2, 1, 2, 10, 
1, 1, 1, 4, 1), technical_lowest = c(7, 8, 6, 5, 9, 10, 4, NA, 
8, 5, 5, 6, 10, 8, 7, 11, 12, 9, 7, 11, 9, 6, 10, 8, 7, 7, 11, 
10, 12, 11, 8, 10, 7, 9, 11, 11, 7, 9, 8, 9, 10, 10, 12, 11, 
5, 12, 13, 8, 8, 9, 9, 11, 12, 7, 7, 5, 5, 11, 10, 9, 6, 6, 8, 
11, 8, 12, 10, 9, 11, 8, 7, 12, 6, 8, 9, 8, 11, 10, 9, 10, 11, 
7, 10, 12, 10, 9, 9, 10, 8, 10, 6, 11, 7, 7, 8), technical_median = c(4.5, 
4.5, 2, 3, 6, 10, 4, NA, 3, 3.5, 2.5, 3, 10, 5, 6, 4.5, 12, 3.5, 
4, 10, 7, 5, 3, 4, 3, 1.5, 3, 6, 12, 7, 6, 4, 4, 8.5, 8.5, 5, 
4, 9, 3, 4, 7, 3.5, 7, 6, 3, 3, 13, 3, 8, 7, 9, 7.5, 10, 4, 2.5, 
3, 2.5, 8, 4.5, 6, 5, 3, 3, 7, 6, 4, 5, 6.5, 11, 4, 5, 3, 3.5, 
2.5, 3.5, 5.5, 11, 9.5, 7, 8, 5, 4, 6, 11.5, 9, 3, 3.5, 5.5, 
4.5, 10, 2.5, 4, 3, 5, 5), series_winner = c(0, 0, 1, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 
0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
1, 0, 0, 0, 0), series_runner_up = c(0, 0, 0, 0, 0, 0, 0, 0, 
1, 1, 0, 1, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 1, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 0, 
0, 0, 0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 1, 0, 
1, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 
1, 0, 0), total_episodes_appeared = c(2, 4, 6, 5, 3, 1, 2, 1, 
6, 6, 4, 8, 3, 7, 5, 8, 1, 8, 5, 2, 3, 6, 10, 8, 9, 10, 10, 5, 
1, 2, 7, 7, 3, 4, 4, 9, 8, 3, 10, 7, 6, 10, 2, 3, 5, 10, 1, 9, 
1, 5, 2, 4, 3, 7, 10, 8, 10, 5, 10, 6, 3, 9, 10, 2, 7, 10, 8, 
4, 1, 10, 5, 10, 8, 10, 10, 4, 1, 2, 3, 6, 9, 7, 5, 2, 3, 5, 
6, 10, 8, 1, 10, 9, 10, 4, 7), first_date_appeared = structure(c(14838, 
14838, 14838, 14838, 14838, 14838, 14838, 14838, 14838, 14838, 
15202, 15202, 15202, 15202, 15202, 15202, 15202, 15202, 15202, 
15202, 15202, 15202, 15566, 15566, 15566, 15566, 15566, 15566, 
15566, 15566, 15566, 15566, 15566, 15566, 15937, 15937, 15937, 
15937, 15937, 15937, 15937, 15937, 15937, 15937, 15937, 15937, 
15937, 16288, 16288, 16288, 16288, 16288, 16288, 16288, 16288, 
16288, 16288, 16288, 16288, 16652, 16652, 16652, 16652, 16652, 
16652, 16652, 16652, 16652, 16652, 16652, 16652, 17037, 17037, 
17037, 17037, 17037, 17037, 17037, 17037, 17037, 17037, 17037, 
17037, 17407, 17407, 17407, 17407, 17407, 17407, 17407, 17407, 
17407, 17407, 17407, 17407), class = "Date"), last_date_appeared = structure(c(14845, 
14859, 14873, 14866, 14852, 14838, 14845, 14838, 14873, 14873, 
15223, 15251, 15216, 15244, 15230, 15251, 15202, 15251, 15230, 
15209, 15216, 15237, 15629, 15615, 15622, 15629, 15629, 15594, 
15566, 15573, 15608, 15608, 15580, 15587, 15958, 15993, 15986, 
15951, 16000, 15979, 15972, 16000, 15944, 15951, 15965, 16000, 
15937, 16344, 16288, 16316, 16295, 16309, 16302, 16330, 16351, 
16337, 16351, 16316, 16351, 16687, 16666, 16708, 16715, 16659, 
16694, 16715, 16701, 16673, 16652, 16715, 16680, 17100, 17086, 
17100, 17100, 17058, 17037, 17044, 17051, 17072, 17093, 17079, 
17065, 17414, 17421, 17435, 17442, 17470, 17456, 17407, 17470, 
17463, 17470, 17428, 17449), class = "Date"), first_date_us = structure(c(NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, 16432, 16432, 16432, 16432, 16432, 16432, 16432, 16432, 16432, 
16432, 16432, 16432, 16432, 16684, 16684, 16684, 16684, 16684, 
16684, 16684, 16684, 16684, 16684, 16684, 16684, 16983, 16983, 
16983, 16983, 16983, 16983, 16983, 16983, 16983, 16983, 16983, 
16983, 17333, 17333, 17333, 17333, 17333, 17333, 17333, 17333, 
17333, 17333, 17333, 17333, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA), class = "Date"), last_date_us = structure(c(NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, 16453, 16488, 16481, 16446, 16495, 16474, 16467, 16495, 16439, 
16446, 16460, 16495, 16432, 16740, 16684, 16712, 16691, 16705, 
16698, 16726, 16747, 16733, 16747, 16712, 16747, 17004, 16997, 
17018, 17025, 16990, 17011, 17025, 17011, 16997, 16983, 17025, 
17004, 17382, 17375, 17382, 17382, 17347, 17333, 17333, 17340, 
17361, 17382, 17368, 17354, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA), class = "Date"), percent_episodes_appeared = c(33.3333333333333, 
66.6666666666667, 100, 83.3333333333333, 50, 16.6666666666667, 
33.3333333333333, 16.6666666666667, 100, 100, 50, 100, 37.5, 
87.5, 62.5, 100, 12.5, 100, 62.5, 25, 37.5, 75, 100, 80, 90, 
100, 100, 50, 10, 20, 70, 70, 30, 40, 40, 90, 80, 30, 100, 70, 
60, 100, 20, 30, 50, 100, 10, 90, 10, 50, 20, 40, 30, 70, 100, 
80, 100, 50, 100, 60, 30, 90, 100, 20, 70, 100, 80, 40, 10, 100, 
50, 100, 80, 100, 100, 40, 10, 20, 30, 60, 90, 70, 50, 20, 30, 
50, 60, 100, 80, 10, 100, 90, 100, 40, 70), percent_technical_top3 = c(50, 
25, 66.6666666666667, 40, 33.3333333333333, 0, 0, 0, 66.6666666666667, 
33.3333333333333, 75, 62.5, 33.3333333333333, 14.2857142857143, 
40, 50, 0, 50, 40, 0, 0, 33.3333333333333, 60, 50, 55.5555555555556, 
70, 60, 0, 0, 50, 0, 14.2857142857143, 0, 0, 0, 33.3333333333333, 
25, 0, 70, 42.8571428571429, 0, 50, 50, 0, 60, 60, 0, 55.5555555555556, 
0, 0, 0, 0, 0, 28.5714285714286, 70, 62.5, 70, 0, 40, 16.6666666666667, 
33.3333333333333, 77.7777777777778, 60, 50, 14.2857142857143, 
40, 37.5, 0, 0, 40, 40, 50, 50, 70, 50, 25, 0, 0, 33.3333333333333, 
16.6666666666667, 33.3333333333333, 28.5714285714286, 20, 0, 
0, 60, 50, 30, 37.5, 0, 60, 44.4444444444444, 60, 0, 28.5714285714286
)), .Names = c("series", "baker_full", "baker", "age", "occupation", 
"hometown", "baker_last", "baker_first", "star_baker", "technical_winner", 
"technical_top3", "technical_bottom", "technical_highest", "technical_lowest", 
"technical_median", "series_winner", "series_runner_up", "total_episodes_appeared", 
"first_date_appeared", "last_date_appeared", "first_date_us", 
"last_date_us", "percent_episodes_appeared", "percent_technical_top3"
), class = c("spec_tbl_df", "tbl_df", "tbl", "data.frame"), row.names = c(NA, 
-95L), spec = structure(list(cols = structure(list(series = structure(list(
    levels = NULL, ordered = FALSE, include_na = FALSE), .Names = c("levels", 
"ordered", "include_na"), class = c("collector_factor", "collector"
)), baker_full = structure(list(), class = c("collector_character", 
"collector")), baker = structure(list(), class = c("collector_character", 
"collector")), age = structure(list(), class = c("collector_double", 
"collector")), occupation = structure(list(), class = c("collector_character", 
"collector")), hometown = structure(list(), class = c("collector_character", 
"collector")), baker_last = structure(list(), class = c("collector_character", 
"collector")), baker_first = structure(list(), class = c("collector_character", 
"collector")), star_baker = structure(list(), class = c("collector_double", 
"collector")), technical_winner = structure(list(), class = c("collector_double", 
"collector")), technical_top3 = structure(list(), class = c("collector_double", 
"collector")), technical_bottom = structure(list(), class = c("collector_double", 
"collector")), technical_highest = structure(list(), class = c("collector_double", 
"collector")), technical_lowest = structure(list(), class = c("collector_double", 
"collector")), technical_median = structure(list(), class = c("collector_double", 
"collector")), series_winner = structure(list(), class = c("collector_double", 
"collector")), series_runner_up = structure(list(), class = c("collector_double", 
"collector")), total_episodes_appeared = structure(list(), class = c("collector_double", 
"collector")), first_date_appeared = structure(list(format = ""), .Names = "format", class = c("collector_date", 
"collector")), last_date_appeared = structure(list(format = ""), .Names = "format", class = c("collector_date", 
"collector")), first_date_us = structure(list(format = ""), .Names = "format", class = c("collector_date", 
"collector")), last_date_us = structure(list(format = ""), .Names = "format", class = c("collector_date", 
"collector")), percent_episodes_appeared = structure(list(), class = c("collector_double", 
"collector")), percent_technical_top3 = structure(list(), class = c("collector_double", 
"collector"))), .Names = c("series", "baker_full", "baker", "age", 
"occupation", "hometown", "baker_last", "baker_first", "star_baker", 
"technical_winner", "technical_top3", "technical_bottom", "technical_highest", 
"technical_lowest", "technical_median", "series_winner", "series_runner_up", 
"total_episodes_appeared", "first_date_appeared", "last_date_appeared", 
"first_date_us", "last_date_us", "percent_episodes_appeared", 
"percent_technical_top3")), default = structure(list(), class = c("collector_guess", 
"collector")), skip = 1), .Names = c("cols", "default", "skip"
), class = "col_spec")))
```

```{r}
bakers_sample <- bakers[10:17,] %>%
  select(baker, star_baker, technical_winner)

bakers_sample
```

```{r}
# Create skills variable with 4 levels
bakers_skill <- bakers_sample %>% 
  mutate(skill = case_when(
    star_baker > technical_winner ~ "super_star",
    star_baker < technical_winner ~ "high_tech",
    star_baker == 0 & technical_winner == 0 ~ NA_character_,
    star_baker == technical_winner  ~ "well_rounded"
  )) %>%
      drop_na(skill)

bakers_skill
```

**Cast A Factor And Examine Levels**

Cast `skill` as a factor:

```{r}
bakers_fct_skill <- bakers_skill %>% 
  mutate(skill = as.factor(skill))

# Examine levels
bakers_fct_skill %>% 
  pull(skill) %>% 
    levels()
```

For more details, go to the [Cast A Column As A Factor](https://econ380w21.github.io/bpAlNw1Ae7YwY9H3f/working-with-data-in-the-tidyverse.html#tame-your-data) section of this chapter.

**Cast Characters As Dates**

Use `lubridate` to parse and cast a date variable within a `mutate()`.

    ?lubridate
```{r}
library(lubridate)

bakers %>% 
  mutate(last_date_appeared = as.character(last_date_appeared))  %>%
  mutate(last_date = ymd(last_date_appeared),
         last_month = month(last_date_appeared, label = TRUE)) %>%
    select(baker, last_date_appeared, last_date, last_month)

```

In the example above, I turned `last_date_appeared` into a `character` type variable first since it was a `date` already. But the point of this is proving the function of `lubridate` in converting `character` into `date` variable.

**Calulate Timespans**

The first step to calculating a timespan in `lubridate` is to make an `interval`, `duration`, `period`, then use division to convert the units to what wanted (like `weeks(x)` or `months(x)`). The `x` refers to the number of time units to be included in the period:

```{r}
bakers_time <- bakers %>% 
    select(baker, first_date_appeared, last_date_appeared)

bakers_time[1:5,]  %>% 
  mutate(time_on_air = interval(first_date_appeared, last_date_appeared),
         weeks_on_air = time_on_air / weeks(1))
```

**String Wrangling**

Use `stringr` package to transform, detect, replace, and remove observations within a data frame:

```{r}
library(stringr)

election[1:7,] %>% 
  mutate(WINNER = str_to_upper(WINNER),
    WINNER = str_replace(WINNER, "MA", "mshazam"),
      WINNER = str_replace(WINNER, "RO", "Bolosho"),
      GROUP_24 = str_detect(group, "24")) %>%
        select(COUNTY, WINNER, GROUP_24)
```
