# Data Manipulation with dplyr

<https://learn.datacamp.com/courses/data-manipulation-with-dplyr>
```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(forcats)
library(stringr)
library(scales)
```

##  Transforming Data with dplyr

**select(), mutate(), filter(), and arrange()**

For more details, go to the [Data Wrangling](https://econ380w21.github.io/bpAlNw1Ae7YwY9H3f/intro-to-the-tidyverse.html#data-wrangling) section of *Intro to the Tidyverse*.

## Aggregating Data

**count()**

A simple way to aggregate data is to count to find out the number of observations. Use `count()`:

```{r}
mtcars %>%
count(cyl, wt = hp, sort = TRUE)

```

Here, `count()` sorted out the distinct observations from the `cyl` variable, the `wt` (weight) would count the total number of `hp` (horse power) for each distinct `cyl` instead of counting the total number of of observations that belongs to each distinct `vyl`.

The `wt` argument basically plug in another column to count instea.

**group_by() And summarize()**

For more details, go to the [Grouping and summarizing](https://econ380w21.github.io/bpAlNw1Ae7YwY9H3f/intro-to-the-tidyverse.html#grouping-and-summarizing) section of *Intro to the Tidyverse*.

**top_n()**

This function select the most extreme observations. The number `1` here select the highest `hp` in each distinct `cyl` observations:

```{r}
mtcars %>%
  select(cyl, hp)  %>%
  mutate(cyl = as.factor(cyl)) %>%
  group_by(cyl) %>%
    top_n(1, hp)
  
```

For more details, go to the [Introduction to Factor Variables](https://econ380w21.github.io/bpAlNw1Ae7YwY9H3f/categorical-data-in-the-tidyverse.html#introduction-to-factor-variables) section of *Categorical Data in the Tidyverse*.

## Selecting and Transforming Data

**select() And rename()***

For more details, go to the [Tame your data](https://econ380w21.github.io/bpAlNw1Ae7YwY9H3f/working-with-data-in-the-tidyverse.html#tame-your-data) section of *Working with Data in the Tidyverse*.

**Transmute()**

The function `transmute()` is like a combination of `select` and `mutate`. It only outputs the selected variables, and allow changing, creating new variables inside the same bracket: 

```{r}
mtcars[1:5,] %>%
  transmute(weight_lbs = wt, weight_kg = weight_lbs / 2.205)

```

## Case Study: The babynames Dataset

```{r}
babynames <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/4984/datasets/a924ac5d86adba2e934d489cb9db446236f62b2c/babynames.rds")))

babynames
```

**Filtering and arranging for one year**

Filter for only the year 1990 and sort the table in descending order of the number of babies born:

```{r}
babynames %>%
  # Filter for the year 1990
  filter(year == 1990) %>%
  # Sort the number column in descending order 
  arrange(desc(number))
```

**Using top_n with babynames**

`filter()` and `arrange()` were used to find the most common names in *one* year. However, `group_by()` and `top_n()` can be used to find the most common name in *every* year:

```{r}
babynames %>%
  group_by(year) %>%
  top_n(1, number)
```

**Visualizing names with ggplot2**

Filter for only the names Steven, Thomas, and Matthew, and assign it to an object called `selected_names`.

The `%in%` operator can be used within `filter()` by including `c()` and a vector of values.

```{r}
selected_names <- babynames %>%
  filter(name %in% c("Steven", "Thomas", "Matthew"))
```

Visualize the three names as a line plot over time, with each name represented by a different color:

```{r}
# Filter for the names Steven, Thomas, and Matthew 
selected_names <- babynames %>%
  filter(name %in% c("Steven", "Thomas", "Matthew"))

# Plot the names using a different color for each name
ggplot(selected_names, aes(x = year, y = number, color = name)) +
  geom_line()
```

**Finding the year each name is most common**

Calculate the total number of people born in that year as `year_total`. Next, use `year_total` to calculate the `fraction` of people born in each year that have each name.

Then, use the `fraction` column, in combination with `top_n()`, to identify the year each name is most common:



```{r}
babynames_fraction <- babynames %>%
  group_by(year) %>%
  mutate(year_total = sum(number)) %>%
  ungroup() %>%
  mutate(fraction = number / year_total) 

# Find the year each name is most common
babynames_fraction %>% 
  group_by(name) %>%
    top_n(1, fraction)

```

**lag() Function**

The `lag()` function can be used to find the differences between two vectors by shifting the vectors to the right:

```{r}
v <- c(1, 3, 6, 14)
v

lag(v)

```

**Changes in popularity of a name**

To find the changes in popularity of the name `"Matthew"` over the years, we will minus the `fraction` by the `lag` of the `fraction` to calculate the `difference` between each year. The `difference` represents the up or down of the `fraction`, which means the popularity increasing or decreasing:

```{r}
babynames_fraction %>%
  filter(name == "Matthew") %>%
  arrange(year) %>%
  mutate(difference = fraction - lag(fraction)) %>%
  arrange(desc(difference))
```
