# Joining Data with dplyr

<https://learn.datacamp.com/courses/joining-data-with-dplyr>
```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(forcats)
library(stringr)
library(scales)
library(lubridate)

sets <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/2e7cb938873ba685957efd822867c86f46dc6b78/sets.rds")))

themes <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/267bcb026359fb2104bf4b717ae166d0bd99c5e6/themes.rds")))

parts <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/cb649926d41ce73490a9bb710e1501a273061723/parts.rds")))

part_categories <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/30fc459770c89e46cce9cce99752ca95fb1d06fe/part_categories.rds")))

inventories <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/2b509dd7a49493ab990580be1845f21f36c46ca0/inventories.rds")))

inventory_parts <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/a49d7bf17fc35fdd1331c01a7f36573800e93cb4/inventory_parts.rds")))

colors <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/aeeda0eaafe6b04c1e42da71a4e9fed7299d096e/colors.rds")))

```

## Joining Tables

**inner_join()**

The `inner_join()` is the key to bring tables together.This function will allow two tables to be joined from the commonly-shared value column(s) on which they should be joined.

In this example, `parts` and `part_categories` are merged by using `part_cat_id` and `id` columns from each dataset, then the `suffix()` added the names to help differentiate the variables:

```{r}
glimpse(parts)
glimpse(part_categories)

parts %>% 
	inner_join(part_categories, by = c("part_cat_id" = "id"), suffix = c("_part", "_category"))

```

Another situation is when wanting to merge two datasets that share the same column(s), using `c()` won't be necessary. Here, the `by =` argument only needs the shared column name: 

```{r}
parts %>%
    inner_join(inventory_parts, by = "part_num")

```

**Joining Multiple Datasets**

Use `inner_join()` and the pipe (`%>%`) to join together multiple datasets.

In this example, `sets`, a table that tells us about each LEGO kit, will be connected with `inventories`, a table that tells us the specific version of a given set, and finally to `inventory_parts`, a table which tells us how many of each part is available in each LEGO kit:

```{r}
sets %>%
	# Add inventories using an inner join 
	inner_join(inventories, by = "set_num") %>%
	# Add inventory_parts using an inner join 
	inner_join(inventory_parts, by = c("id" = "inventory_id"))
```

To utilize this, join an additional table, `colors`, which tell the color of each part in each set, to answer the question, "what is the most common color of a LEGO piece?"

```{r}
# Count the number of colors and sort
sets %>%
	inner_join(inventories, by = "set_num") %>%
	inner_join(inventory_parts, by = c("id" = "inventory_id")) %>%
	inner_join(colors, by = c("color_id" = "id"), suffix = c("_set", "_color")) %>%
		count(name_color, sort = TRUE)
```

From the output, `Black` seems to be the most common LEGO piece.

`inner_join()` *ONLY* keeps the perfectly matched observations between two connected datasets.

## Left and Right Joins

**left_join()**

`left_join()` keeps *ALL* the observations from the left dataset and keep *ONLY* the matched observations from the right-side dataset.

Combine the `star_destroyer` and `millennium_falcon` tables with the suffixes `_falcon` and `_star_destroyer`:

```{r}
inventory_parts_joined <- inventories %>%
  inner_join(inventory_parts, by = c("id" = "inventory_id")) %>%
  select(-id, -version) %>%
  arrange(desc(quantity))

millennium_falcon <- inventory_parts_joined %>%
  filter(set_num == "7965-1")

star_destroyer <- inventory_parts_joined %>%
  filter(set_num == "75190-1")

millennium_falcon %>%
 left_join(star_destroyer, by = c("part_num", "color_id"), suffix = c("_falcon", "_star_destroyer"))

```

From the output, the `quantity_falcon` kept all the observations, and the `quantity_star_destroyer` only kept the matched ones, the `NA`s are the unmatched ones.

**right_join()**

`right_join()` keeps *ALL* the observations from the right dataset and keep *ONLY* the matched observations from the left-side dataset.

In this example, count the `part_cat_id` from `parts`, before using a `right_join` to join with `part_categories.` This is to know the count of `part_cat_id` in parts, and also to see if there are any `part_cat_id` observations not available in `parts` by using `filter()`:

```{r}
parts %>%
	count(part_cat_id) %>%
	right_join(part_categories, by = c("part_cat_id" = "id")) %>%
	# Filter for NA
	filter(is.na(n))

```

Here, the left-side dataset is the `n` column, which contains a `NA` observation, and the `name` column is the right-sde dataset which retains all the observations. 

**Joining tables to themselves**

Tables can be joined to themselves!

In the `themes` dataset, there are two `columns` id and `parent_id`, which has a connection to each other. On the `parent_id` side, `Arctic Technic`, 	`Competition`, `Expert Builder`,	`Model` are assigned as `1` on `parent_id` column, which are sub-branches of the `Technic`, which has `id` of `1` on the left-side. 

Then, the `Airport`, `Construction`, `Farm`, `Fire`, `Harbor` are assigned as `5` on `parent_id` column, which are the sub-branches of `Model`, which has `id` of `5` of the left-side.

This table has a hierarchical table.

```{r}
themes
```

```{r}
themes %>% 
	# Inner join the themes table
	inner_join(themes, by = c("id" = "parent_id"), suffix = c("_parent", "_child")) %>%
	# Filter for the "Harry Potter" parent name 
	filter(name_parent == "Harry Potter")
```

The code chunk above outputs all the sub-branches that belong to the `Harry Potter`. 

**Joining themes to their grandchildren**

`inner_join()` can merge `themes` to a filtered version of itself again to establish a connection between our last join's children and their children. Use another inner join to combine themes again with itself:

```{r}
# Join themes to itself again to find the grandchild relationships
themes %>% 
  inner_join(themes, by = c("id" = "parent_id"), suffix = c("_parent", "_child")) %>%
  inner_join(themes, by = c("id_child" = "parent_id"), suffix = c("_parent", "_grandchild"))

```

**Left-joining a table to itself**

Some `themes` might not have any sub-branches at all, which means they won't be included in the `inner_join()`. Identify those with a `left_join()` and a `filter()`:

```{r}
themes %>% 
  # Left join the themes table to its own children
  left_join(themes, by = c("id" = "parent_id"), suffix = c("_parent", "_child")) %>%
  # Filter for themes that have no child themes
  filter(is.na(name_child))

```
The output above shows all the theme groups that doesn't have any sub-branches.

## Full, Semi, and Anti Joins

**full_join()**

left_join and right_join keeps all the observations in one of the two sides. full_join() keeps all the observations on *BOTH* sides:

```{r}
inventory_sets_themes <- inventory_parts_joined %>%
  inner_join(sets, by = "set_num") %>%
  inner_join(themes, by = c("theme_id" = "id"), suffix = c("_set", "_theme"))

batman <- inventory_sets_themes %>%
  filter(name_theme == "Batman")
batman_parts <- batman %>%
  count(part_num, color_id, wt = quantity)

star_wars <- inventory_sets_themes %>%
  filter(name_theme == "Star Wars")
star_wars_parts <- star_wars %>%
  count(part_num, color_id, wt = quantity)
```

The variables above set up the data to prepare for the `full_join` to find out the difference pieces used in `batman` and `star_wars`:
```{r}
batman_parts %>%
  # Combine the star_wars_parts table 
  full_join(star_wars_parts, by = c("part_num", "color_id"), suffix = c("_batman", "_star_wars")) %>%
  # Replace NAs with 0s in the n_batman and n_star_wars columns 
  replace_na(list(n_batman = 0, n_star_wars = 0))

```

**semi_join()**

`semi_join()` filter and output the observations that of the left-side dataset that matches with the right-side. (ONLY show the left-side observations that arematched, not showing both datasets).

Let's focus on the `batwing` dataset, determine which parts are in both the `batwing` and `batmobile` sets.

```{r}
batmobile <- inventory_parts_joined %>%
  filter(set_num == "7784-1") %>%
  select(-set_num)

batwing <- inventory_parts_joined %>%
  filter(set_num == "70916-1") %>%
  select(-set_num)

# Filter the batwing set for parts that are also in the batmobile set
batwing %>%
    semi_join(batmobile, by = "part_num")

```

**anti_join()**

The opposite of `semi_join` is `anti_join()`. It shows the observations that are in the left-side dataset but is not in the right-side dataset. In other words, what observations are in the first table but not in the second table? 

Let's focus on the `batwing` dataset, determine which sets are in one, but not the other.

```{r}
# Filter the batwing set for parts that aren't in the batmobile set
batwing %>%
    anti_join(batmobile, by = "part_num")

```

**Aggregating sets to look at their differences**

To compare two individual `sets`, and the kinds of LEGO pieces that comprise them, aggregate the data into separate themes. Additionally, add a column to understand the percentages of specific pieces that are part of each set, rather than looking at the numbers of pieces alone.

```{r}
inventory_parts_themes <- inventories %>%
  inner_join(inventory_parts, by = c("id" = "inventory_id")) %>%
  arrange(desc(quantity)) %>%
  select(-id, -version) %>%
  inner_join(sets, by = "set_num") %>%
  inner_join(themes, by = c("theme_id" = "id"), suffix = c("_set", "_theme"))

batman_colors <- inventory_parts_themes %>%
  filter(name_theme == "Batman") %>%
  group_by(color_id) %>%
  summarize(total = sum(quantity)) %>%
  mutate(percent = total / sum(total))

star_wars_colors <- inventory_parts_themes %>%
  filter(name_theme == "Star Wars") %>%
  group_by(color_id) %>%
  summarize(total = sum(quantity)) %>%
  mutate(percent = total / sum(total))

```

**Combining sets**

Prior to visualizing the data, combine these tables to be able to directly compare the themes' colors. Join the `batman_colors` and `star_wars_colors` tables; be sure to include all observations from both tables. Replace the `NA`s in the `total_batman` and `total_star_wars` columns.

Add a `difference` column that calculates the difference between `percent_batman` and `percent_star_wars`, and a `total` column, which is the sum of `total_batman` and `total_star_wars.`
Add a `filter` to select observations where `total` is at least `200`.

```{r}
colors_joined <- batman_colors %>%
  # Join the Batman and Star Wars colors
  full_join(star_wars_colors, by = "color_id", suffix = c("_batman", "_star_wars")) %>%
  # Replace NAs in the total_batman and total_star_wars columns
  replace_na(list(total_batman = 0, total_star_wars = 0)) %>%
  inner_join(colors, by = c("color_id" = "id")) %>%
  # Create the difference and total columns
  mutate(difference = percent_batman - percent_star_wars,
         total = total_batman + total_star_wars) %>%
  # Filter for totals greater than 200
  filter(total >= 200) %>%
  mutate(name = fct_reorder(name, difference)) 

colors_joined

```

**Visualizing the difference: Batman and Star Wars**

Create a bar plot using the `colors_joined` table to display the most prominent colors in the Batman and Star Wars themes, with the bars colored by their `name`.

```{r}
color_palette <- structure(c("#05131D", "#0055BF", "#C91A09", "#F2CD37", "#FFFFFF", 
"#E4CD9E", "#958A73", "#C91A09", "#F5CD2F", "#582A12", "#A0A5A9", 
"#6C6E68", "#CC702A", "#898788", "#A0BCAC"), .Names = c("Black", 
"Blue", "Red", "Yellow", "White", "Tan", "Dark Tan", "Trans-Red", 
"Trans-Yellow", "Reddish Brown", "Light Bluish Gray", "Dark Bluish Gray", 
"Medium Dark Flesh", "Flat Silver", "Sand Green"))

```

```{r}
# Create a bar plot using colors_joined and the name and difference columns
ggplot(colors_joined, aes(name, difference, fill = name)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = color_palette, guide = FALSE) +
  labs(y = "Difference: Batman - Star Wars")

```

## Case Study: Joins on Stack Overflow Data

```{r}
questions <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/89d5a716b4f41dbe4fcda1a7a1190f24f58f0e47/questions.rds")))

tags <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/207c31b235786e73496fd7e58e416779911a9d98/tags.rds")))

question_tags <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/966938d665c69bffd87393b345ea2837a94bab97/question_tags.rds")))

answers <- readRDS(gzcon(url("https://assets.datacamp.com/production/repositories/5284/datasets/6cb9c039aa8326d98de37afefa32e1c458764638/answers.rds")))

```

**Left-joining questions and tags**

Three of the Stack Overflow survey datasets are `questions`, `question_tags`, and `tags`:

`questions`: an ID and the score, or how many times the question has been upvoted; the data only includes R-based questions

`question_tags`: a tag ID for each question and the question's id

`tags`: a tag id and the tag's name, which can be used to identify the subject of each question, such as ggplot2 or dplyr

In this exercise, stitch together these datasets and replacing `NA`s in important fields:

```{r}
# Replace the NAs in the tag_name column
questions_with_tags <- questions %>%
  left_join(question_tags, by = c("id" = "question_id")) %>%
  left_join(tags, by = c("tag_id" = "id")) %>%
  replace_na(list(tag_name = "only-r"))

questions_with_tags

```

**Comparing scores across tags**

Let's do a quick bit of analysis on it! You'll use familiar `dplyr` verbs like `group_by`, `summarize`, `arrange`, and `n` to find out the average score of the most asked questions:

```{r}
questions_with_tags %>%
	# Group by tag_name
	group_by(tag_name) %>%
	# Get mean score and num_questions
	summarize(score = mean(score),
          	  num_questions = n()) %>%
	# Sort num_questions in descending order
	arrange(desc(num_questions))

```

**What tags never appear on R questions?**

The `tags` table includes all Stack Overflow tags, but some have nothing to do with `R`. Filter for just the tags that never appear on an R question with `anti_join`:

```{r}
# Using a join, filter for tags that are never on an R question
tags %>%
    anti_join(question_tags, by = c("id" = "tag_id"))

```

**Finding gaps between questions and answers**

Join together `questions` with `answers` to measure the time between questions and answers.

Use an `inner_join` to combine the `questions` and `answers` tables using the suffixes `"_question"` and `"_answer"`, respectively.

Subtract `creation_date_question` from `creation_date_answer` within the `as.integer()` function to create the `gap` column.

```{r}
questions %>%
	# Inner join questions and answers with proper suffixes
	inner_join(answers, by = c("id" = "question_id"), suffix = c("_question", "_answer")) %>%
	# Subtract creation_date_question from creation_date_answer to create gap
	mutate(gap = as.integer(creation_date_answer - creation_date_question)) 

```

**Joining question and answer counts**

Determine how many questions actually yield answers. Count the number of answers for each question, then join the answers counts with the `questions` table:

```{r}
answer_counts <- answers %>%
    count(question_id, sort = TRUE)

question_answer_counts <- questions %>%
    left_join(answer_counts, by = c("id" = "question_id")) %>%
    replace_na(list(n = 0))

```

**Average answers by question**

Determine, on average, how many answers each questions gets. Some of the important variables from this table include: `n`, the number of answers for each question, and `tag_name`, the name of each tag associated with each question.

```{r}
tagged_answers <- question_answer_counts %>%
    inner_join(question_tags, by = c("id" = "question_id")) %>%
    inner_join(tags, by = c("tag_id" = "id"))

tagged_answers %>%
	# Aggregate by tag_name
    group_by(tag_name) %>%
	# Summarize questions and average_answers
    summarize(questions = n(),
              average_answers = mean(n)) %>%
	# Sort the questions in descending order
    arrange(desc(questions))

```

**bind_rows()**

The `bind_row` function basically merges two tables together, or stack them into one big dataset instead of leaving them as two seperate tables.

**Binding and counting posts with tags**

Combine the `questions_with_tags` and `answers_with_tags` tables into `posts_with_tags`.

Add a `year` column to the `posts_with_tags` table, then aggregate to count posts by `type`, `year`, and `tag_name`.

```{r}
questions_with_tags <- questions %>%
  inner_join(question_tags, by = c("id" = "question_id")) %>%
  inner_join(tags, by = c("tag_id" = "id"))

answers_with_tags <- answers %>%
  inner_join(question_tags, by = "question_id") %>%
  inner_join(tags, by = c("tag_id" = "id"))

# Combine the two tables into posts_with_tags
posts_with_tags <- bind_rows(questions_with_tags %>% mutate(type = "question"),
                              answers_with_tags %>% mutate(type = "answer"))

# Add a year column, then aggregate by type, year, and tag_name
by_type_year_tag <- posts_with_tags %>%
  mutate(year = year(creation_date)) %>%
  count(type, year, tag_name)

by_type_year_tag

```

The code chunk outputs a dataset of posts (either questions or answers) that are tagged with their created dates, and a count for that post.

**Visualizing questions and answers in tags**

Create a plot to examine the information that the table contains about questions and answers for the `dplyr` and `ggplot2` tags. 

`Filter` the `by_type_year_tag` table for the `dplyr` and `ggplot2` tags.

Create a line plot with that filtered table that plots the frequency (`n`) over time, colored by question/answer and faceted by tag.

```{r}
# Filter for the dplyr and ggplot2 tag names 
by_type_year_tag_filtered <- by_type_year_tag %>%
  filter(tag_name %in% c("dplyr", "ggplot2"))

# Create a line plot faceted by the tag name 
ggplot(by_type_year_tag_filtered, aes(year, n, color = type)) +
  geom_line() +
  facet_wrap(~ tag_name)
```

